Topics in Algorithms

### 2018-01-08 project/paper.tex
Added code for figure
Added second figure to figure to show delta increase

\usepackage[margin=1in]{geometry}  % set the margins to 1in on all sides
\usepackage{graphicx}              % to include figures
\usepackage{amsmath,bm}            % great math stuff
\usepackage{amsfonts}              % for blackboard bold, etc
\usepackage{amsthm}                % better theorem environments
\usepackage{listings}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage[linesnumbered,ruled,vlined,algosection]{algorithm2e}
\usepackage{parskip} 			   % no paragraph indentation

@@

% Reference til Mikkel/Zwick paper - hans query time og 'vores' forbedrede query time - forbedring af konstruktion. Forbedring i querytime, uden at det påvirker space/konstruktionstid.

>>>>

\usepackage[margin=1in]{geometry}  % set the margins to 1in on all sides
\usepackage{graphicx}              % to include figures
\usepackage{amsmath,bm}            % great math stuff
\usepackage{amsfonts}              % for blackboard bold, etc
\usepackage{amsthm}                % better theorem environments
\usepackage{listings}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage[linesnumbered,ruled,vlined,algosection]{algorithm2e}
\usepackage{parskip} 			   % no paragraph indentation
\usepackage{subcaption}

@@

\begin{figure}
\begin{subfigure}[b]{\textwidth}
\begin{tikzpicture}
\filldraw (0,0) circle (2pt) node[align=left,   below] {$u$};
\filldraw (10,0) circle (2pt) node[align=right,  below] {$v$};
\filldraw[fill=gray] (4,3) circle (2pt) node[align=left, above] {$p_j(u)$};
\filldraw[fill=white] (8,3.45) circle (2pt) node[align=left, above] {$p_{j+1}(v)$};
\coordinate (u) at (0,0) ;
\coordinate (v) at (10,0);
\coordinate (pu) at (4,3);
\coordinate (pv) at (8, 3.45);
\draw[dashed] (v) circle [radius=4];
\draw (u) -- (pu) node[pos=0.5, above, sloped] {$d_G(u,p_j(u))$};
\draw (u) -- (v) node[pos=0.5, below, sloped] {$d_G(u,v))$};
\draw (v) -- (pv) node[pos=0.5, below, sloped] {$d_G(v, p_{j+1}(v)$};
\draw[dotted] (v) -- (pu) node[pos=0.75, below, sloped] {$d_G(v, p_{j}(u)$};
\end{tikzpicture}
\caption{$(j)$th iteration\label{j1}}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
\begin{tikzpicture}
\filldraw (0,0) circle (2pt) node[align=left,   below] {$v$};
\filldraw (10,0) circle (2pt) node[align=right,  below] {$u$};
\filldraw[fill={rgb:black,1;white,3}] (5,4.9) circle (2pt) node[align=left, above] {$p_{j+2}(v)$};
\filldraw[fill=white] (8,3.45) circle (2pt) node[align=left, above] {$p_{j+1}(u)$};
\coordinate (v) at (0,0) ;
\coordinate (u) at (10,0);
\coordinate (pv) at (5,4.9);
\coordinate (pu) at (8, 3.45);
\begin{scope}
    \clip (0,6) rectangle (7,-1);
    \draw[dashed] (v) circle [radius=7];
\end{scope}

\draw (v) -- (pv) node[pos=0.5, above, sloped] {$d_G(v,p_{j+2}(v))$};
\draw (v) -- (u) node[pos=0.5, below, sloped] {$d_G(v,u))$};
\draw (u) -- (pu) node[pos=0.5, below, sloped] {$d_G(u, p_{j+1}(u)$};
\draw[dotted] (v) -- (pu) node[pos=0.5, below, sloped] {$d_G(v, p_{j+1}(u)$};
\end{tikzpicture}
\caption{$(j+1)$th iteration.\label{j2}}
\end{subfigure}
\caption{Two consecutive iterations of the while loop in $dist_k$. Both sampled points of $u$, $p_j(u)$ in Fig. \ref{j1} and $p_{j+1}(u)$ in Fig. \ref{j2}, are not in $B_v$ and therefore $j$ is not $(u,v)$-terminal.}
\end{figure}
% Reference til Mikkel/Zwick paper - hans query time og 'vores' forbedrede query time - forbedring af konstruktion. Forbedring i querytime, uden at det påvirker space/konstruktionstid.
